
%-------------------------
% Resume in Latex (Compact Version with GPA + SAT)
% Author : Anirudh Tiwary
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{comment}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.25in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting - tighter spacing
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\pdfgentounicode=1

% Custom Commands (tight spacing)
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-3pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-6pt}}
\newcommand{\resumeProjectHeading}[2]{\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=2pt, leftmargin=0.12in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}, itemsep=1pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Anirudh Tiwary} \\[-0.1pt]
    \small 201-744-5517 $|$ 
    \href{mailto:anitiwary87@gmail.com}{\underline{anitiwary87@gmail.com}} $|$
    \href{https://github.com/ani-tiwary}{\underline{github.com/ani-tiwary}} $|$
    \href{https://www.linkedin.com/in/ani-tiwary}{\underline{linkedin.com/in/ani-tiwary}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rutgers University}{New Brunswick, NJ}
      {B.S. Mathematics, Computer Science, and Philosophy \textbar\ GPA: 3.83}{2024 \textbf{---} 2027}
      \resumeItemListStart
        \resumeItem{Coursework: Computer Architecture, Algorithms, Data Structures, Linear Optimization, Calculus IV}
        \resumeItem{Involvement: Rutgers Economics Labs Analyst, USACS Technical Blog Writer, Rutgers Chess Team Player}
      \resumeItemListEnd
    \resumeSubheading
      {Academy for Information Technology}{Scotch Plains, NJ}
      {High School Diploma – Computer Science Track \textbar\ SAT: 1570}{2020 \textbf{---} 2024}
      \resumeItemListStart
        \resumeItem{Coursework: Mathematical Statistics \& Data Science, Advanced Software Development}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.12in, label={}, itemsep=1pt]
    \small{\item{
     \textbf{Languages}{: Java, Python, JavaScript, HTML/CSS, TypeScript, SQL, GDScript} \\
     \textbf{ML \& Data Tools}{: Language Models, Pandas, Scikit-learn, TensorFlow, NumPy, Seaborn} \\
     \textbf{Frameworks \& Platforms}{: Supabase, Next.js, React, Tailwind CSS, Redis, Flask, Node.js} \\
     \textbf{Other Tools}{: Linux, Git, OAuth, Android Studio}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

   \resumeSubheading
  {Software Engineer \textbf{---} Scarlet Sync}{Apr. 2025 \textbf{---} Present}
  {Rutgers University}{New Brunswick, NJ}
  \resumeItemListStart
    \resumeItem{Co-founded and scaled (\textbf{750+ users}) Rutgers’ first course scheduling platform featuring conflict detection, automated registration, and collaborative tools.}
    \resumeItem{Architected production-ready \textbf{Next.js + Supabase} system generating \textbf{5K+ schedules in under 2s} with secure \textbf{OAuth}-based authentication.}
    \resumeItem{Implemented \textbf{Redis-based caching and Pub/Sub} for real-time seat updates and query acceleration, enabling low-latency scheduling performance.}
  \resumeItemListEnd


    \resumeSubheading
      {Machine Learning Research Assistant \textbf{---}  Aresty Research Program}{May 2025 \textbf{---} Present}
      {Rutgers University}{New Brunswick, NJ}
      \resumeItemListStart
        \resumeItem{Developed a \textbf{machine learning pipeline} using \textbf{Python, Pandas, and Scikit-learn} to predict railway track degradation for NJTransit, achieving\textbf{ 73\% accuracy} with Ridge Regression.}
        \resumeItem{Enabled \textbf{predictive public policy planning} with \textbf{25–30\% cost reduction potential} through advanced preprocessing and feature engineering.}
        \resumeItem{Engineered \textbf{19 temporal, statistical, and spatial features} from \textbf{1,566 measurements across 348 track segments}, implementing chronological validation to prevent data leakage.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Yoga Pose Analysis Web Application} $|$ \emph{Flask, OpenCV, MediaPipe, TensorFlow}}{Jan. 2025 \textbf{---} Apr. 2025}
      \resumeItemListStart
        \resumeItem{Developed a real-time computer vision tool analyzing 17+ human keypoints to evaluate yoga form with \textbf{95\% pose classification accuracy}.}
        \resumeItem{Integrated \textbf{Flask REST API} and WebSocket streaming for live camera feedback and cross-platform deployment.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Markov Chain Text Generator} $|$ \emph{Python, NumPy, Matplotlib}}{Jul. 2023 \textbf{---} Aug. 2023}
      \resumeItemListStart
        \resumeItem{Built a trigram Markov text generator with \textbf{Kneser–Ney smoothing} and \textbf{subword tokenization}, enabling context-aware phrase synthesis across heterogeneous datasets.}
        \resumeItem{Streamlined matrix operations and caching to achieve a \textbf{40\%} improvement in sampling throughput and stable perplexity across \textbf{50K+} unique tokens.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------ACCOLADES-----------
\section{Accolades}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Medalist \textbf{---}  ASA Data Challenge}{Sep. 2023 \textbf{---} Jan. 2024}
      {American Statistical Association}{}
      \resumeItemListStart
        \resumeItem{Ranked \textbf{Top 3 nationwide} among 500+ teams for quantitative modeling of Stack Overflow developer data using \textbf{Python (Pandas, Seaborn, Scikit-learn)}.}
        \resumeItem{Performed multivariate regression and sentiment clustering to identify key predictors of coding bootcamp success, and \textbf{identified top-weighted linguistic and demographic features} driving performance variability.}
      \resumeItemListEnd

    \resumeSubheading
      {State Finalist \textbf{---}  Coding \& Programming}{Jan. 2024 \textbf{---} Mar. 2024}
      {Future Business Leaders of America}{}
      \resumeItemListStart
        \resumeItem{Designed a full-stack \textbf{React + Flask} platform aggregating internship and volunteer opportunities with automated data scraping and \textbf{MongoDB}-backed search.}
        \resumeItem{Implemented real-time keyword search using \textbf{Elasticsearch} APIs, improving data retrieval speed by \textbf{70\%}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
